Seasonality in governing dynamics at submesoscales in the Kuroshio Extension

### 2016-06-28 writeup/rocha_etal.tex
Small edit.
Small edits

The April vorticity-strain jPDF has a shape characteristic of submesoscale turbulence
 (see figures \ref{fig3}a-c). The alignment of vorticity and strain $\alpha \sim \pm\zeta$
 with strong positive skewness are fingerprints of submesoscale fronts
 \citep{shcherbina_etal2013,mcwilliams2016}. The shape of the vorticity-strain
 jPDF is similar for hourly, daily-averaged, and residual velocities, although
 the vorticity skewness reduces 1.4 to 1.13 from hourly to daily-averaged.
 Thus wintertime submesoscale surface velocity is strongly dominated by submesoscale turbulence --- this is true even for
 superinertial submesoscale currents. The hourly velocity fields are significantly
ageostrophic as depicted by the jPDF of vorticity-Laplacian of SSH
(figure \ref{fig3}g). While there is certainly much to be
learned using quasi-geostrophic models to study submesoscale turbulence, claims that
the submesoscale turbulence is dominantly in geostrophic balance
are overstated \citep{sasaki_etal2014,callies_etal2016}; only the daily-averaged fields
are largely
in  geostrophic balance (the jPDF of daily-averaged vorticity vs. Laplacian of SSH
is an ellipse with large eccentricity with main axis tilted by 45$^\circ$; figure \ref{fig3}h).

>>>>

The April vorticity-strain jPDF has a shape characteristic of submesoscale turbulence
 (see figures \ref{fig3}a-c). The alignment of vorticity and strain $\alpha \sim \pm\zeta$
 with strong positive skewness are fingerprints of submesoscale fronts
 \citep{shcherbina_etal2013,mcwilliams2016}. The shape of the vorticity-strain
 jPDF is similar for hourly, daily-averaged, and residual velocities, although
 the vorticity skewness reduces 1.4 to 1.13 from hourly to daily-averaged.
 Thus wintertime submesoscale surface velocity is strongly dominated by submesoscale turbulence --- this is true even for
 superinertial submesoscale currents. The hourly velocity fields are significantly
ageostrophic as depicted by the jPDF of vorticity-Laplacian of SSH
(figure \ref{fig3}g). Even in April, only the daily-averaged fields
are largely
in  geostrophic balance (the jPDF of daily-averaged vorticity vs. Laplacian of SSH
is an ellipse with large eccentricity and main axis tilted by 45$^\circ$; figure \ref{fig3}h).

%While there is certainly much to be
%learned using quasi-geostrophic models to study submesoscale turbulence, claims that
%the submesoscale turbulence is dominantly in geostrophic balance
%are overstated \citep{sasaki_etal2014,callies_etal2016};
